\documentclass[line]{res}
\usepackage{cite}
\begin{document}
\name{Mathew T. Prokos}
\address{724 East 2nd St, Royal Oak, MI 48067}
\address{mathew.prokos@gmail.com}
\phone{(248) 635-4128}

\begin{resume}
\section{OBJECTIVE}
    These are my objectives
\section{QUALIFICATIONS}
    {\sl Operating Systems:} VxWorks 6.6, VxWorks 653, Linux, FreeBSD\\
    {\sl Languages:} C, C++, ADA95, x86 Assembly, MC++, Java, OpenGL, Python, Shell, Clojure 
\section{WORK EXPERIENCE}
    Oasis Advanced Engineering \hfill Auburn Hills, MI\\
    Senior Software Engineer
    \begin{itemize} 
    \item Designed and implemented vehicle component simulators
    \item Designed distributed real-time replay software
    \item Preformed application porting from AIX to linux
    \end{itemize}
\section{EDUCATION} 
    {\sl Michigan State University 2001-2005 \hfill East Lansing, MI}\\
    Bachelor of Computer Science Engineering\\
    Grade Point Average 3.68\\
    {\sl Oakland University 2011-Present \hfill Auburn Hills, MI}\\
    Masters Computer Science\\
    Grade Point Average 4.0
\section{PUBLICATIONS} 
    Paliwal, K.K., Shannon, B.J., Lyons, J.G. and K.K. W\'ojcicki,
    ``Speech-signal-based frequency warping'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 16, No. 4, pp. 319-322, 2009.

\vspace{-2mm}
    Paliwal, K.K. and K.K. W\'ojcicki,
    ``Effect of analysis window duration on speech intelligibility'',
    \textsl{IEEE Signal Process. Lett.}, Vol. 15, pp. 785-788, 2008.

\end{resume}
\end{document}

